### 2021-11-16 input/proposal.tex
very start of algo

\subsection{Implementation and complexity}

Algorithm~\ref{algo:ascast} provides the instructions of \NAME that
implement three-phase purge and eventual forwarding of best to enable
dynamic consistent partitioning. For the sake of simplicity, it does
not handle multiple sessions nor optimisation such as message packing.

\begin{algorithm}
  \input{input/algoascast.tex}
  \caption{\label{algo:ascast}\NAME at \Process~$p$.}
\end{algorithm}

As stated in Theorem~\ref{theo:dcp}, every \process must purge stale
messages.  To identify staleness, each \process maintains a vector of
versions that associates the respective known local counter of each
known source, or has-been source. Its size increases linearly with the
number of sources that the \process has ever known, which is the
number of \processes in the system $\mathcal{O}(V)$ in the worst case.
Nevertheless, following the principles of scoped broadcast, we expect
that every \process only acknowledges a small subset of sources.  In
addition, each message carries the identifier and counter of each
\node that forwarded it. Again, following the principles of scoped
broadcast, we expect that versioned paths remain small. Using these
data structures, each \process delivers and forwards only new messages
that improve their best known partition (see
Line~\ref{line:ascast_improve}).

This vector of versions constitutes a summary of known progress of
other \nodes. It discards stale messages and it enables detecting
possible inconsistencies in message delivery: the current best
partition comes from a neighbor that just delivered a stale message
(see Line~\ref{line:ascast_detect}). Figure~\ref{fig:problem} shows
that such a behavior may hide a delete notification. The detecting
\process must act to reflect this possible change: all \processes
whose last message comes from the detecting \process must remove it
and accept the competition of other \processes. Since this behavior is
similar to that of source deletion, we implement it in a similar way.

A \process that removes its self-appointed status of source, or
detects a possible inconsistency, increments its local counter and
disseminates a delete notification message $\delta_{s, c}$
piggybacking its identifier $s$ and counter $c$. Any \process that
receives such delete notification delivers and forwards it if its best
message contains the has-been source or detector associated to a lower
counter (see Line~\ref{line:ascast_delete}). This allows $\delta$
messages to quickly reach every downstream \process.

As stated in Theorem~\ref{theo:dcp}, dynamic consistent partitioning
not only requires eventual purging of stale messages, but also the
retrieval of the best up-to-date partitions.  In that regard, $\delta$
messages have a dual use: since they already reach the borders of
their partition by design, they trigger a competition when reaching
bordering.  When a \process receives a delete notification from a
neighbor $q$ but does not deliver it, it assumes that the just
received $\delta$ message purged possibly stale messages, creating a
gap that its own best partition could help fill. Consequently, it
sends to $q$ its own best $\alpha$ message (see
Line~\ref{line:ascast_echo}).

\begin{algorithm}
  \input{input/algoedges.tex}
  \caption{\label{algo:edges}\NAME at \Process~$p$ in dynamic networks.}
\end{algorithm}

Algorithm~\ref{algo:edges} enables dynamic consistent partitioning in
dynamic networks where \processes can join, leave, or crash at any
time. Removing a \process is equivalent to removing all its edges, and
adding a \process is equivalent to add as many edges as necessary.
Adding an edge between two \processes may only improve the shortest
path of one of these \processes. Therefore, it triggers a competition
between the two \processes. If one or the other \process improves, the
propagation of $\alpha$ messages operates normally.  Removing an edge
between two \processes may invalidate the shortest path of one of
involved \processes plus downstream \processes. As a side effect,
removing an edge may also impair the propagation of a partition
delete. To implement this behavior, \NAME uses its implementation of
$\delta$ messages. This enables \NAME even in dynamic networks subject
to physical partitioning.

%% \NAME guarantees dynamic consistent partitioning by making extensive
%% use of \process-to-\process communications. It requires
%% \begin{inparaenum}[(i)]
%% \item purging stale control information, hence propagating $\delta$
%%   messages; and
%% \item retrieving the closest source, hence propagating $\alpha$
%%   messages.
%% \end{inparaenum}
In terms of number of messages, in the average case, a \process $i$
chosen uniformly at random among all \processes creates a logical
partition. Its messages $\alpha_i$ spread through the network until
reaching \processes that belong to another partition closer to
them. This splits partitions in half on average. Overall, the $a^{th}$
new partition comprises \smash{$\mathcal{O}(\frac{|V|}{2^{\lfloor
      \log_2 a \rfloor}})$} \processes. This decreases every new
partition until reaching one \process per new partition: its
source. The average number of messages per \process is
\smash{$\mathcal{O}(\frac{\overline{|O|}}{2^{\lfloor \log_2 a
      \rfloor}})$}, where \smash{$\overline{|O|}$} is the average
number of neighbors per \process.
% \TODO{Multiple receipt and
% multiple
%  delivery imply more messages (receipt bounded by $|O|$ as well).}
Deleting the $a^{th}$ partition generates twice as many messages as
creating the $a^{th}$ partition: $\delta$ messages travel through the
partition, then $\alpha$ messages compete to fill the gap.  Overall,
the communication complexity shows that \NAME scales well to the
number of partitions.
%% In the
%% worst-case, every new partition includes all but one \process
%% belonging to the previous partition. The total number of messages
%% after the $a^{th}$ new partition is $\mathcal{O}(\overline{|O|}\cdot
%% a^2)$. As for the average-case, the number of messages for the
%% partition deletion is identical to the number of messages of the
%% corresponding partition creation.
%% \begin{algorithm}[h!]
%%   \input{input/algoedges.tex}
%%   \caption{\label{algo:edges}\NAME at \Process~$p$ in dynamic networks.}
%% \end{algorithm}
Next Section provides the details of our simulations that assess the
proposed implementation.

>>>>

\subsection{Lazy partitioning}
\label{subsec:lazy}

\NAME enables indexing the closest replica of each \process without
flooding the whole network when a new replica appears or disappears.
Nevertheless, every node must partake in the indexing of each
content. When the networks accounts for billions of content, this
raises scalability issues. Inspired by the Internet topology that
comprises tens of thousands of interconnected autonomous systems
serving billions of people~\cite{nur2018crossas}, we want to further
lock-down traffic by leveraging the edges of networks as barriers, and
enable on-demand indexing.

To enable cross-network indexing, we designed and implemented \NAMEC
(stands for both \underline{cross} \underline{a}utonomous
\underline{s}ystems and \underline{ex}tended \underline{a}daptive
\underline{s}coped broad\underline{cast}). The main idea behind \NAMEC
is that every node maintains two \NAME:
\begin{inparaenum}[(i)]
\item the first maintaining the closest source intra-AS and
  acknowledges the interests of its AS;
\item the second maintaining the closest source cross-AS that also
  competes against the local closest source.
\end{inparaenum}
\NAMEC enables nodes to discard irrelevant indexes while maintaining
the closest source between connected ASes. \TODO{This section
  describes our proposal.}

\TODO{Added invariant: global is always smaller than local when they
  exist.}
